Deep Reinforcement Learning for Conservation Decisions

### 2021-05-17 manuscript/manuscript.Rmd
Small updates
Overhauling with writing from alternate

Note that this formalism extends to an infinite horizon case when $T= \infty$.
While there are RL methods to deal with infinite horizon cases, we will only finite horizon or episodic MDP and POMDPs.

@@

@@

@@

-->
```{=latex}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Algorithm & Description & Model & Policy & Action Space & State Space \\
\hline
MBPO & Model-based Policy Optimization & Model-based & On-policy& &\\
\hline
MCTS & Monte Carlo Tree Search & Model-based & Either & & \\
\hline
A2C  & Advantage Actor Critic & Model-free & On-policy& &\\
\hline
A3C  & Asynchronous A2C & Model-free & On-policy & &\\
\hline
TRPO  & Trust Region Policy Optimization & Model-free & On-policy & &\\
\hline
PPO  & Proximal Policy Optimization & Model-free & On-policy & &\\
\hline
DQN & Deep Q Networks & Model-free & Off-policy& &\\
\hline
DDPG & Deep Deterministic Policy Gradient & Model-free & Off-policy & &\\
\hline
TD3 & Twin Delayed DDPG & Model-free & Off-policy & &\\
\hline
SAC & Soft Actor Critic & Model-free & Off-policy & &\\
\hline
IMPALA & Importance Weighted Actor Learner & Model-free & Off-policy & &\\
\hline
APE-X & Distributed Prioritized Experience Replay & Model-free & Off-policy & & \\
\hline
\end{tabular}
\end{center}
```

# Examples

>>>>

@@

# RL Background

Note that this formalism extends to an infinite horizon case when $T= \infty$.
While there are RL methods to deal with infinite horizon cases, we will only present methods for finite horizon or episodic MDP and POMDPs.

@@

<!-- Kari: I think we need more background on what a neural network is, how it fits in, and what other options are - maybe use examples of hyperparameters that would be in all RL approaches not just those that use neural nets -->

@@

-->
```{=latex}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Algorithm & Description & Model & Policy & Action Space & State Space \\
\hline
MBPO & Model-based Policy Optimization [@mbpo] & Model-based & On-policy & Continuous & Continuous\\
\hline
MCTS & Monte Carlo Tree Search [@suttonbarto] & Model-based & Either & & \\
\hline
A2C  & Advantage Actor Critic [@a2c] & Model-free & On-policy& &\\
\hline
A3C  & Asynchronous A2C & Model-free [@a3c] & On-policy & &\\
\hline
TRPO  & Trust Region Policy Optimization [@trpo] & Model-free & On-policy & &\\
\hline
PPO  & Proximal Policy Optimization [@ppo] & Model-free & On-policy & &\\
\hline
DQN & Deep Q Networks [@dqn] & Model-free & Off-policy& &\\
\hline
DDPG & Deep Deterministic Policy Gradient [@ddpg] & Model-free & Off-policy & &\\
\hline
TD3 & Twin Delayed DDPG [@td3] & Model-free & Off-policy & &\\
\hline
SAC & Soft Actor Critic [@sac] & Model-free & Off-policy & &\\
\hline
IMPALA & Importance Weighted Actor Learner [@impala] & Model-free & Off-policy & &\\
\hline
APE-X & Distributed Prioritized Experience Replay [@apex] & Model-free & Off-policy & & \\
\hline
\end{tabular}
\end{center}
```
# Examples
